A seamless, client-centric programming model for type safe web applications

### 2014-05-07 paper.tex
Rephrase RemoteValue introduction.

\begin{code}
liftServerIO :: IO a -> App (Remote a)
\end{code}

In contrast to \lstinline!liftIO!, the result value of \lstinline!liftServerIO!
is wrapped in the abstract \lstinline!Remote! type. As the name implies,
values of this type live exclusively on the server. In order to inspect such a
value is needs to be extracted somehow, something which is only possible using
a single function:

\begin{code}
use :: Remote a -> Server a
\end{code}

Therein lies the secret to restricting \lstinline!liftServerIO! to the
server: the only function capable of turning a \lstinline!Remote! value into
a useful one lives in the server monad. Any client side code is thus free to
completely ignore executing computations lifted using \lstinline!liftServerIO!;
since the result of a server lifted computation is never observable on the
client, the client has no obligation to even produce such a value.
Figure \ref{lst:good-state} shows how to make proper use of server side state.

>>>>

\begin{code}
liftServerIO :: IO a -> App (RemoteValue a)
\end{code}

In contrast to \lstinline!liftIO!, the result value of \lstinline!liftServerIO!
is wrapped in the abstract \lstinline!RemoteValue! type. As the name implies,
values of this type live exclusively on the server. In order to inspect such a
value is needs to be extracted somehow, something which is only possible using
a single function:

\begin{code}
use :: RemoteValue a -> Server a
\end{code}

Therein lies the secret to restricting \lstinline!liftServerIO! to the
server: the only function capable of turning a \lstinline!RemoteValue! into
one that can be inspected lives in the server monad. Any client side code is
thus free to completely ignore executing computations lifted using
\lstinline!liftServerIO!; since the result of a server lifted computation is
never observable on the client, the client has no obligation to even produce
such a value. Figure \ref{lst:good-state} shows how to make proper use of
server side state.
